Supermassive black hole and host bulge affairs \\ II. The red and blue sequence in the $M_{\rm BH} - M_{\rm *,sph}$ diagram.

### 2015-05-08 papers/MbhMsph/mm.tex
friday

\begin{abstract}
{\bf limit of 250 words, currently there are 229 words, there's room for 21 words. 
Things not mentioned: 1) the galaxy components (more appropriate for data paper?????), 
2) $3.6\rm~\mu m$ \emph{Spitzer} satellite imagery, minimally affected by dust and star formation 
3) updated linear regressions (symmetrical, to be compared with theoretical expectations, and non-symmetrical, to be used to predict black hole masses) 
for S\'ersic/core-S\'ersic galaxies and for different morphological types (E/S0, Sp)}\\
We present correlations between black hole mass, $M_{\rm BH}$, 
and both the host galaxy's and spheroid's infrared luminosity, $L_{\rm gal}$ and $L_{\rm sph}$, 
and the spheroid's stellar mass, $M_{\rm *,sph}$,
built upon a high-quality data set.
Our sample, the largest ever used, counts 66 local galaxies with a dynamical measurement of $M_{\rm BH}$.
%Luminosities come from high signal-to-noise $3.6\rm~\mu m$ \emph{Spitzer} satellite imagery, 
%which is minimally affected by dust and star formation. 
%These luminosities were derived from our state-of-the-art multicomponent galaxy decompositions, 
%that take into account bulges, disks, bars, spiral arms, rings, haloes, extended or unresolved nuclear sources and partially depleted cores, 
%and that -- for the first time -- were checked to be consistent with the galaxy kinematics. 
Spheroid luminosities come from high signal-to-noise $3.6\rm~\mu m$ \emph{Spitzer} satellite imagery, 
and were derived from our state-of-the-art {\bf ``many-component''} galaxy decompositions 
that, for the first time, were checked to be consistent with the galaxy kinematics. 
Previous studies have used galaxy samples that were overwhelmingly dominated by high-mass, early-type objects.
Instead, our sample includes 17 spiral galaxies, half of which have $M_{\rm BH} < 10^7\rm~M_\odot$, 
and allows us to better investigate the poorly studied low-mass end of the $M_{\rm BH} - M_{\rm *,sph}$ correlation.
%We provide updated linear regressions 
%(symmetrical, to be compared with theoretical expectations, and non-symmetrical, to be used to predict black hole masses) 
%for S\'ersic/core-S\'ersic galaxies and for different morphological types (E/S0, Sp). 
The bulges of early-type (E + S0) galaxies follow $M_{\rm BH} \propto M_{\rm *,sph}^{1.04 \pm 0.10}$, 
consistent with a dry-merging formation scenario,
and define a tight \emph{red sequence} with intrinsic scatter $\epsilon_{(Y|X)} = 0.43 \pm 0.06\rm~dex$.
On the other hand, the bulges of late-type (Sp) galaxies define a much steeper \emph{blue sequence}, 
with $M_{\rm BH} \propto M_{\rm *,sph}^{2-3}$, 
indicating that gas-rich processes feed the black hole more efficiently than the host bulge. 
We additionally report that: i) S\'ersic galaxies follow $M_{\rm BH} \propto M_{\rm *,sph}^{1.48 \pm 0.20}$, a less steep sequence than previously reported; 
ii) bulges with S\'ersic index $n_{\rm sph}<2$, argued by some to be pseudo-bulges, 
are not offset to lower $M_{\rm BH}$ from the correlation defined by bulges with $n_{\rm sph}>2$; 
iii) $L_{\rm sph}$ and $L_{\rm gal}$ correlate equally well with $M_{\rm BH}$, in terms of intrinsic scatter, only for early-type galaxies; 
once reasonable numbers of spiral galaxies are included, the correlation with $L_{\rm sph}$ is better than that with $L_{\rm gal}$.

@@

\keywords{keywords}

@@

More than two and a half decades ago, 
\cite{dressler1989} foresaw a ``rough scaling of black hole mass with the mass of the spheroidal component'', 

@@

His ``rough scaling'' was a premature version of the nowadays popular correlation between black hole mass, $M_{\rm BH}$,  

@@

\citep{yee1992,kormendyrichstone1995,magorrian1998,marconihunt2003,haringrix2004}. 

@@

consistent with a dry-merging formation scenario. 

@@

(\citealt{ferrareseford2005,lauer2007,graham2007,graham2008bar,gultelkin2009,sani2011,beifiori2012,erwingadotti2012,

@@

used similar galaxy samples, which remained dominated by high-mass, early-type systems having $M_{\rm BH} \gtrsim 0.5 \times 10^8~\rm M_\odot$, 

@@

or noticed that low-mass spheroids were downwards offset from the relation traced by their high-mass counterparts 

@@

as it does with the bulge luminosity. \\

@@

which can be described with a single power-law ($M_{\rm BH} \propto \sigma^5$) 

@@

being $L_{\rm sph} \propto \sigma^5$ at the luminous end \citep{schechter1980,malumuthkrishner1981,vonderlinden2007,liu2008}, 

@@

That is, the $M_{\rm BH} - L_{\rm sph}$ relation should be better described by a ``broken'', rather than a single, power-law, 
having $M_{\rm BH} \propto L_{\rm sph}^{2.5}$ at the low-luminosity end, 

@@

When \cite{graham2012bent} pointed out this overlooked inconsistency, 

@@

and attributed the change in slope (from quadratic to linear) to their different formation mechanisms. 

@@

in which the mass of the black hole increases more rapidly than the mass of its host spheroid ($M_{\rm BH} \propto L_{\rm sph}^{2.5}$). 

@@

using a mean statistical correction based on each object's morphological type and disc 

@@

their large sample size allowed them to obtain a reasonably ensemble average correction.}. 
However, this mean statistical correction was obtained from the results of non-modern bulge/disk decompositions. 

@@

but follow the two times steeper relation traced by the S\'ersic spheroids. 
Using data from \cite{jiang2011a}, \cite{grahamscott2015} showed that this appears to extend to spheroids with even lower black hole masses 

@@

using state-of-the-art galaxy decompositions (Savorgnan \& Graham 2015, \emph{in preparation}, hereafter \emph{Paper I}) 

@@

(instead of simple bulge/disk decompositions) without incurring in significant parameter degeneracies. 

@@

which is an excellent proxy for the stellar mass, superior to the $K-$band (\citealt{sheth2010} and references therein).

@@

which allows us to accurately constrain the slope of the correlation at the low-mass end.

@@

representing a notable improvement over the past studies dominated by early-type systems. 
In a forthcoming paper, we will explore the relation between black hole mass and bulge dynamical mass, 

@@

This paper is structured as follows...

@@

(by GS13 or \citealt{rusli2013bhmassesDM}) at the time we started this project, 
and for which we were able to obtain useful bulge parameters from $3.6\rm~\mu m$ \emph{Spitzer} satellite imagery. 
Bulge magnitudes were derived from our state-of-the-art galaxy decompositions, which take into account 

@@

to confirm the presence of rotationally supported components in most early-type galaxies, 

@@

\emph{Paper I} will present the dataset used here, 

@@

give details about the data reduction process and the sophisticated galaxy modelling technique that we developed, 
discuss how we estimated the uncertainties\footnote{By comparing, for each of our galaxies, the measurements of the bulge magnitude 
obtained by different authors with that obtained by us, we estimated the uncertainties on the bulge magnitudes 
with a method that takes into account systematic errors. 

@@

the radial extent of the surface brightness profile and its sampling. 
These factors are not included in popular 2D fitting codes which report only the random errors associated with their fitted parameters. 

@@

on the bulge magnitudes, and illustrate the individual 66 galaxy decompositions. \\
Bulge luminosities\footnote{Absolute luminosities were calculated 
assuming a $3.6\rm~\mu m$ solar absolute magnitude of $3.25\rm~mag$ \citep{sani2011}.} 
were first converted into stellar masses using a constant $3.6\rm~\mu m$ mass-to-light ratio, $\Gamma_{3.6} = 0.6$ \citep{meidt2014}.
We then explored a more sophisticated way to compute mass-to-light ratios, 

@@

within one galaxy's effective radius.} were taken from 

@@

underestimated\footnote{These four cases will be discussed in \emph{Paper I}.}, 

@@

Following GS13, we assumed a fixed uncertainty ($0.25\rm~mag$) for $MAG_{\rm gal}$. \\
The morphological classification (E = elliptical; E/S0 = elliptical/lenticular; S0 = lenticular; S0/Sp = lenticular/spiral; Sp = spiral; merger) 

@@

Throughout the paper, we will refer to early-type galaxies (E+S0) and late-type galaxies (Sp). 
Galaxies classified as E/S0 are obviously included in the early-type bin, 
whereas galaxies classified as S0/Sp or as mergers are included in neither the early- nor the late-type bin.\\

@@

or as S\'ersic if $\sigma < 166\rm~km~s^{-1}$. \\

@@

\section{Analysis}
\label{sec:anal}
We performed a linear regression analysis of the $M_{\rm BH} - L_{\rm gal}$ (see Table \ref{tab:lreggal}), 
$M_{\rm BH} - L_{\rm sph}$ (see Table \ref{tab:lregsph}) and $M_{\rm BH} - M_{\rm *,sph}$ (see Table \ref{tab:lregmass}),
using the BCES code from \cite{akritasbershady1996}. 
We also repeated the analysis with the FITEXY routine \citep{press1992}, as modified by \cite{tremaine2002}, 
and the Bayesian estimator {\tt linmix\_err} \citep{linmixerr}. 
All these three linear regression routines account for the intrinsic scatter, 
but only the last two allow to quantify it.
%Because the BCES routine {\bf AL: did you wanna write (correctly) this sentence for me please? 
%can give biased results (wrong slope) when the scatter is comparable to the range of the data},
%we checked that the best-fit parameters obtained with the BCES code were consistent with those output by the modified FITEXY code.
We report linear regressions, both symmetrical and non-symmetrical, 
for S\'ersic/core-S\'ersic and for early/late-type galaxies.
Symmetrical regressions are meant to be compared with theoretical expectations, 
whereas non-symmetrical $(Y|X)$ regressions -- 
since they minimize the scatter in the $\log M_{\rm BH}$ direction -- 
can be used to predict black hole masses.

@@

\subsection{Black hole mass -- galaxy luminosity}
Figure \ref{fig:mbhmaggal} illustrates the $M_{\rm BH} - L_{\rm gal}$ diagram.
Four spiral galaxies had their total luminosities underestimated (see Section \ref{sec:data}) 
and thus are not included in the linear regression analysis (see Table \ref{tab:lreggal}). \\
Upon analyzing a sample of 35 galaxies, among which only four were classified as spiral galaxies, 
\cite{lasker2014anal} claimed that the $M_{\rm BH} - L_{\rm sph}$ and $M_{\rm BH} - L_{\rm gal}$ relations, 
which they fit with a single power-law, have consistent intrinsic scatter.
Here, instead, thanks to our double-sized galaxy sample that includes 17 spiral galaxies, 
we show that the claim made by \cite{lasker2014anal} is valid only for early-type galaxies. 
The $M_{\rm BH} - L_{\rm sph}$ correlation for all galaxies, irrespective of their morphological type, 
has intrinsic scatter $\epsilon_{(Y|X)} = 0.51 \pm 0.06\rm~dex$ (forward linear regression) 
and $\epsilon_{(X|Y)} = 0.60 \pm 0.09\rm~dex$ (inverse linear regression), 
whereas the $M_{\rm BH} - L_{\rm gal}$ correlation for all galaxies has $\epsilon_{(Y|X)} = 0.63 \pm 0.07\rm~dex$ 
and $\epsilon_{(X|Y)} = 0.91 \pm 0.17\rm~dex$.
However, when considering only early-type galaxies, 
we find that the $M_{\rm BH} - L_{\rm sph}$ and $M_{\rm BH} - L_{\rm gal}$ relations have the same level of intrinsic scatter. 
%($\epsilon_{(Y|X)} = 0.41 \pm 0.06\rm~dex$ and $\epsilon_{(X|Y)} = 0.51 \pm 0.10\rm~dex$ 
%against $\epsilon_{(Y|X)} = 0.43 \pm 0.06\rm~dex$ and $\epsilon_{(X|Y)} = 0.53 \pm 0.10\rm~dex$).
Because the value of the intrinsic scatter depends on the amplitude of the uncertainties associated to the luminosities\footnote{The 
smaller (larger) the uncertainties, the larger (smaller) the intrinsic scatter.}, 
we tested the robustness of our last conclusion by increasing/decreasing the errors associated to $L_{\rm gal}$ 
(that we originally assumed to be $0.25\rm~mag$) and repeating the linear regression analysis. 
We decided to vary only the errors associated to $L_{\rm gal}$ 
because we consider the uncertainties associated to $L_{\rm sph}$ trustworthy, since they have been estimated with an advanced method 
that takes into account the systematic errors related to the galaxy decomposition process. 
We found that the $M_{\rm BH} - L_{\rm sph}$ and $M_{\rm BH} - L_{\rm gal}$ relations for early-type galaxies 
have inconsistent intrinsic scatter when assuming an error $\geq 0.7\rm~mag$ on $L_{\rm gal}$. 
Because such error is larger than the typical error on $L_{\rm sph}$ estimated by us 
and, in general, is significantly larger than the uncertainties on $L_{\rm gal}$ that are typically assumed in the literature, 
we conclude that our determination of the intrinsic scatter is reliable, 
and that $M_{\rm BH}$ correlates equally well with $L_{\rm sph}$ and $L_{\rm gal}$ only for early-type galaxies, but not for all (early+late) galaxies.
As \cite{lasker2014anal} pointed out, from the observer's perspective, measuring galaxy luminosities is obviously easier and faster 
than performing accurate galaxy decompositions to obtain bulge luminosities. 
This, combined with our last conclusion, suggests that one should prefer the galaxy luminosity over the bulge luminosity 
to predict black hole masses when dealing with samples of elliptical and lenticular galaxies only.

\begin{figure}[h]
\begin{center}
\includegraphics[width=\columnwidth]{images/mbh_vs_mag_tot.pdf}
\caption{Black hole mass plotted against $3.6\rm~\mu m$ galaxy absolute magnitude. 
Symbols are coded according to the galaxy morphological type: red circle = E, red star = E/S0, 
red upward triangle = S0, blue downward triangle = S0/Sp, blue square = Sp, black diamond = merger. 
Empty symbols represent core-S\'ersic spheroids, whereas filled symbols are used for S\'ersic spheroids. 
Four spiral galaxies had their magnitudes overestimated and are shown as upper limits. 
The red dashed line indicates the BCES bisector linear regression for 45 early-type galaxies (E+S0), 
with the red shaded area denoting its $1\sigma$ uncertainty. 
We were not able to obtain any meaningful linear regression for the late-type (Sp) galaxies. 
$M_{\rm BH}$ correlates equally well with $L_{\rm sph}$ and $L_{\rm gal}$ only for early-type galaxies, 
but not for all (early+late) galaxies. }
\label{fig:mbhmaggal}
\end{center}
\end{figure}

\begin{table*}
\centering
\caption{Linear regression analysis of the $M_{\rm BH} - MAG_{\rm gal}$ diagram.}
\begin{tabular}{llccccc}
\tableline\tableline
{\bf Subsample (size)} & {\bf Regression} & $\boldsymbol \alpha$ & $\boldsymbol \beta$ & $\boldsymbol \langle MAG_{\rm gal} \rangle$ & $\boldsymbol \epsilon$ & $\boldsymbol \Delta$ \\ 
\tableline 
\\
  & \multicolumn{6}{l}{$\log[M_{\rm BH}/{\rm M_\odot}] = \alpha + \beta[(MAG_{\rm gal} - \langle MAG_{\rm gal} \rangle)/{\rm mag}]$} \\ [0.5em]
 All (62)               & BCES $(Y|X)$   & $8.26 \pm 0.08$ & $-0.49 \pm 0.06$ & $-24.78$ & $-$ & $0.64$ \\
                        & BCES $(X|Y)$   & $8.26 \pm 0.12$ & $-1.01 \pm 0.15$ & $-24.78$ & $-$ & $0.92$ \\
                        & BCES Bisector  & $8.26 \pm 0.09$ & $-0.72 \pm 0.07$ & $-24.78$ & $-$ & $0.71$ \\
                        & mFITEXY $(Y|X)$  & $8.26^{+0.08}_{-0.08}$ & $-0.49^{+0.06}_{-0.07}$ & $-24.78$ & $0.61^{+0.07}_{-0.06}$ & $0.64$ \\
                        & mFITEXY $(X|Y)$  & $8.26^{+0.11}_{-0.12}$ & $-1.03^{+0.13}_{-0.16}$ & $-24.78$ & $0.88^{+0.10}_{-0.08}$ & $0.93$ \\
                        & mFITEXY Bisector & $8.26^{+0.10}_{-0.10}$ & $-0.73^{+0.09}_{-0.10}$ & $-24.78$ & $-$    & $0.71$ \\
                        & {\tt linmix\_err} $(Y|X)$  & $8.26 \pm 0.09$ & $-0.49 \pm 0.07$ & $-24.78$ & $0.63 \pm 0.07$ & $0.64$ \\
                        & {\tt linmix\_err} $(X|Y)$  & $8.26 \pm 0.12$ & $-1.02 \pm 0.15$ & $-24.78$ & $0.91 \pm 0.17$ & $0.93$ \\
                        & {\tt linmix\_err} Bisector & $8.26 \pm 0.10$ & $-0.72 \pm 0.15$ & $-24.78$ & $-$    & $0.71$ \\ [0.5em]

@@

We now come to the $M_{\rm BH} - L_{\rm sph}$ diagram, which is shown in Figure \ref{fig:mbhmagsph}, 
and whose linear regression analysis is presented in Table \ref{tab:lregsph}. \\

@@

Instead, the slope that we determined for S\'ersic spheroids ($M_{\rm BH} \propto L_{\rm sph}^{1.53 \pm 0.20}$) 
is shallower than that found by GS13 ($M_{\rm BH} \propto L_{\rm sph}^{2.73 \pm 0.55}$). 

@@

Our bulge-to-total ratios for low-luminosity S\'ersic spheroids ($MAG_{\rm sph} \gtrsim -22 \rm~mag$) 

@@

while the bulge-to-total ratios of GS13 were derived from simple literature bulge/disk decompositions 

@@

On the other side, our bulge-to-total ratios for high-luminosity S\'ersic spheroids ($MAG_{\rm sph} \lesssim -24 \rm~mag$) 

@@

In this case, the host systems are early-type galaxies that feature intermediate-scale disks\footnote{Intermediate-scale disks are 

@@

We have seen that the change in slope of the $M_{\rm BH} - L_{\rm sph}$ correlation -- 

@@

We remark on the unsuitability of the Pearson's and Spearman's correlation coefficients because 

>>>>

\begin{abstract}
In our first paper, we performed a detailed (i.e.~bulges, disks, bars, spiral arms, rings, haloes, nuclei, cores, etc.) 
decomposition of 66 galaxies, with directly measured black hole masses, 
that had been imaged at $3.6\rm~\mu m$ with \emph{Spitzer}.
Our sample is the largest to date and, for the first time, the decompositions were checked to be consistent with the galaxy kinematics.
Here we present correlations between the black hole mass, $M_{\rm BH}$, 
and the host spheroid (and galaxy) luminosity, $L_{\rm sph}$ (and $L_{\rm gal}$), 
and also stellar mass, $M_{\rm *,sph}$.
Most previous studies have used galaxy samples that were overwhelmingly dominated by high-mass, early-type objects.
Instead, our sample includes 17 spiral galaxies, half of which have $M_{\rm BH} < 10^7\rm~M_\odot$, 
and allows us to better investigate the poorly studied low-mass end of the $M_{\rm BH} - M_{\rm *,sph}$ correlation.
The bulges of early-type (E + S0) galaxies follow $M_{\rm BH} \propto M_{\rm *,sph}^{1.04 \pm 0.10}$, 
consistent with a dry-merging formation scenario,
and define a tight \emph{red sequence} with intrinsic scatter $\epsilon_{(Y|X)} = 0.43 \pm 0.06\rm~dex$.
On the other hand, the bulges of late-type (Sp) galaxies define a much steeper \emph{blue sequence}, 
with $M_{\rm BH} \propto M_{\rm *,sph}^{2-3}$, 
indicating that gas-rich processes feed the black hole more efficiently than the host bulge as they grow. 
We additionally report that: i) S\'ersic galaxies follow $M_{\rm BH} \propto M_{\rm *,sph}^{1.48 \pm 0.20}$, a less steep sequence than previously reported; 
ii) bulges with S\'ersic index $n_{\rm sph}<2$, argued by some to be pseudo-bulges, 
are not offset to lower $M_{\rm BH}$ from the correlation defined by bulges with $n_{\rm sph}>2$; 
and iii) $L_{\rm sph}$ and $L_{\rm gal}$ correlate equally well with $M_{\rm BH}$, in terms of intrinsic scatter, only for early-type galaxies; 
once reasonable numbers of spiral galaxies are included, the correlation with $L_{\rm sph}$ is better than that with $L_{\rm gal}$. {\bf 241 words}

@@

\keywords{\bf keywords}

@@

A quarter of a century ago, 
\cite{dressler1989} foresaw a ``rough scaling of black hole mass with the mass of the spheroidal component'' of galaxies, 

@@

\cite{yee1992} also announced a relation between what was effectively black hole mass and galaxy mass for bright early-type galaxies.
This ``rough scaling'' was a premature version of the nowadays popular correlation between black hole mass, $M_{\rm BH}$,  

@@

\citep{kormendyrichstone1995,magorrian1998,marconihunt2003,haringrix2004}. 

@@

consistent with a dry-merging formation scenario which would build and maintain a linear scaling. 

@@

(\citealt{ferrareseford2005,lauer2007,graham2007,gultelkin2009,sani2011,beifiori2012,erwingadotti2012,

@@

continued to use galaxy samples dominated by high-mass, early-type systems having $M_{\rm BH} \gtrsim 0.5 \times 10^8~\rm M_\odot$, 

@@

or noticed that low-mass spheroids were offset to the lower right of the relation traced by their high-mass counterparts 

@@

as it does with the bulge luminosity. 
Now we roughly double the sample. \\

@@

which can be described with a single power-law ($M_{\rm BH} \propto \sigma^{5-6}$) 

@@

with $L_{\rm sph} \propto \sigma^{5-6}$ at the luminous end \citep{schechter1980,malumuthkrishner1981,vonderlinden2007,lauer2007lumell,liu2008}, 

@@

The $M_{\rm BH} - L_{\rm sph}$ relation should therefore be better described by a ``broken'', rather than a single, power-law, 
with $M_{\rm BH} \propto L_{\rm sph}^{2.5}$ at the low-luminosity end, 

@@

When \cite{graham2012bent} pointed out this overlooked inconsistency between these linear and bent relations, 

@@

and attributed the change in slope (from super-quadratic to linear) to their different formation mechanisms. 

@@

in which the mass of the black hole increases more rapidly than the mass of its host spheroid ($M_{\rm BH} \propto L_{\rm sph}^{2.5}$). \\

@@

using a mean statistical bulge-to-total ratio based on each object's morphological type and disc 

@@

their large sample size allowed them to obtain a reasonable $M_{\rm BH} - L_{\rm sph}$ relation for the ensemble.}. 
This mean statistical correction was obtained from the results of non-modern bulge/disk decompositions. 

@@

but follow the steeper relation traced by the S\'ersic spheroids. 
Using bulge/disk decomposition data from \cite{jiang2011a}, 
\cite{grahamscott2015} derived the host spheroid masses 
and showed that the steeper $M_{\rm BH} - M_{\rm *,sph}$ extends to these spheroids with even lower black hole masses 

@@

using state-of-the-art galaxy decompositions (Savorgnan \& Graham 2015, hereafter \emph{Paper I}) 

@@

(instead of simple bulge/disk decompositions). 

@@

which is an excellent proxy for the stellar mass, superior to the $K-$band (\citealt{sheth2010}, and references therein).

@@

which allows us to constrain the slope of the correlation at the low-mass end.

@@

representing a notable improvement over past studies dominated by early-type systems. 
In a forthcoming paper, we will explore the relation between the black hole mass and the bulge dynamical mass, 

@@

{\bf This paper is structured as follows... }

@@

(by GS13 or \citealt{rusli2013bhmassesDM}) at the time that we started this project, 
and for which we were able to obtain useful spheroid parameters from $3.6\rm~\mu m$ \emph{Spitzer} satellite imagery. 
Spheroid magnitudes were derived from our state-of-the-art galaxy decompositions, which take into account 

@@

to confirm the presence of rotationally supported disk components in most early-type galaxies, 

@@

\emph{Paper I} presents the dataset used here, 

@@

including details about the data reduction process and the galaxy modelling technique that we developed. 
It also discusses how we estimated the uncertainties\footnote{By comparing, for each of our galaxies, the measurements of the bulge magnitude 
obtained by different authors with that obtained by us, we estimated the uncertainties on the bulge magnitudes, 
in effect taking into account systematic errors. 

@@

the radial extent of the surface brightness profile and one's sampling of this. 
Most of these factors are not included in popular 2D fitting codes which report only the random errors associated with their fitted parameters. 

@@

on the bulge magnitudes, and presents the individual 66 galaxy decompositions, 
along with a comparison and discussion of past decompositions. \\
Bulge luminosities\footnote{Following \cite{sani2011}, absolute luminosities were calculated 
assuming a $3.6\rm~\mu m$ solar absolute magnitude of $3.25\rm~mag$.} 
(Table \ref{tab:sample}) from \emph{Paper I} were converted into stellar masses 
using a constant $3.6\rm~\mu m$ mass-to-light ratio, $\Gamma_{3.6} = 0.6$ \citep{meidt2014}.
We additionally explored a more sophisticated way to compute mass-to-light ratios, 

@@

within each galaxy's effective radius.} were taken from 

@@

underestimated\footnote{These four cases are discussed in \emph{Paper I}.}, 

@@

Following GS13, we assumed a fixed uncertainty ($0.25\rm~mag$) for the absolute galaxy magnitude $MAG_{\rm gal}$. \\
The morphological classification (E = elliptical; E/S0 = elliptical/lenticular; S0 = lenticular; S0/Sp = lenticular/spiral; Sp = spiral; and merger) 

@@

Throughout this paper, we will refer to early-type galaxies (E+S0) and late-type galaxies (Sp). 
Two galaxies classified as E/S0 are obviously included in the early-type bin, 
whereas two galaxies classified as S0/Sp or another two classified as mergers are included in neither the early- nor the late-type bin.\\

@@

or as S\'ersic if $\sigma < 166\rm~km~s^{-1}$. 
Galaxies with velocity dispersions between these bands had high-resolution images available. \\

@@

\section{Analysis}
\label{sec:anal}
We performed a linear regression analysis of the $M_{\rm BH} - L_{\rm gal}$ (see Table \ref{tab:lreggal}), 
$M_{\rm BH} - L_{\rm sph}$ (see Table \ref{tab:lregsph}) and $M_{\rm BH} - M_{\rm *,sph}$ (see Table \ref{tab:lregmass}) data,
using the BCES code from \cite{akritasbershady1996}. 
We also repeated the analysis using both the FITEXY routine \citep{press1992}, as modified by \cite{tremaine2002}, 
and the Bayesian estimator {\tt linmix\_err} \citep{linmixerr}. 
All of these three linear regression routines account for the intrinsic scatter, 
but only the last two allow one to quantify it.
%Because the BCES routine {\bf AL: did you wanna write (correctly) this sentence for me please? 
%can give biased results (wrong slope) when the scatter is comparable to the range of the data},
%we checked that the best-fit parameters obtained with the BCES code were consistent with those output by the modified FITEXY code.
We report linear regressions, both symmetrical and non-symmetrical, 
for S\'ersic/core-S\'ersic and for early/late-type galaxies.
Symmetrical regressions are meant to be compared with theoretical expectations, 
whereas non-symmetrical direct ($M_{\rm BH}|X$) regressions -- 
which minimize the scatter in the $\log(M_{\rm BH})$ direction -- 
can be used to predict black hole masses.

@@

\subsection{Black hole mass -- galaxy luminosity}
The $M_{\rm BH} - L_{\rm gal}$ diagram is shown in Figure \ref{fig:mbhmaggal}.
Four spiral galaxies had their total luminosities underestimated (see Section \ref{sec:data}) 
and thus are not included in the linear regression analysis (see Table \ref{tab:lreggal}). \\
\cite{lasker2014anal} analyzed a sample of 35 galaxies, among which only four were classified as spiral galaxies, 
and claimed that the $M_{\rm BH} - L_{\rm sph}$ and $M_{\rm BH} - L_{\rm gal}$ relations, 
which they fit with a single power-law, have consistent intrinsic scatter.
Here, instead, thanks to our galaxy sample that includes 17 spiral galaxies, 
we show that the claim made by \cite{lasker2014anal} is valid only for early-type galaxies. 
Our $M_{\rm BH} - L_{\rm sph}$ relation for 66 galaxies, irrespective of their morphological type, 
has an intrinsic scatter $\epsilon_{(Y|X)} = 0.51 \pm 0.06\rm~dex$ (forward linear regression) 
and $\epsilon_{(X|Y)} = 0.60 \pm 0.09\rm~dex$ (inverse linear regression), 
whereas our $M_{\rm BH} - L_{\rm gal}$ relation for 62 ($=66-4$) galaxies has $\epsilon_{(Y|X)} = 0.63 \pm 0.07\rm~dex$ 
and $\epsilon_{(X|Y)} = 0.91 \pm 0.17\rm~dex$.
However, when considering only early-type galaxies, 
we find that the $M_{\rm BH} - L_{\rm sph}$ and $M_{\rm BH} - L_{\rm gal}$ relations have the same level of intrinsic scatter. \\
%($\epsilon_{(Y|X)} = 0.41 \pm 0.06\rm~dex$ and $\epsilon_{(X|Y)} = 0.51 \pm 0.10\rm~dex$ 
%against $\epsilon_{(Y|X)} = 0.43 \pm 0.06\rm~dex$ and $\epsilon_{(X|Y)} = 0.53 \pm 0.10\rm~dex$).
Because the value of the intrinsic scatter depends on the size of the uncertainties associated to the absolute magnitudes\footnote{The 
smaller (larger) the uncertainties, the larger (smaller) the intrinsic scatter.}, 
we tested the robustness of our last conclusion by increasing/decreasing the errors associated with $L_{\rm gal}$ 
(we originally assumed $0.25\rm~mag$). 
%We decided to vary only the errors associated to $L_{\rm gal}$ 
%because we consider the uncertainties associated to $L_{\rm sph}$ trustworthy, since they have been estimated with an advanced method 
%that takes into account the systematic errors related to the galaxy decomposition process. 
We found that the $M_{\rm BH} - L_{\rm sph}$ and $M_{\rm BH} - L_{\rm gal}$ relations for early-type galaxies 
have inconsistent intrinsic scatter when assuming an error $\geq 0.7\rm~mag$ on $L_{\rm gal}$. 
Because such error is larger than the typical error on $L_{\rm sph}$ estimated by us 
and, in general, is significantly larger than the uncertainties on $L_{\rm gal}$ that are typically assumed in the literature, 
we conclude that our determination of the intrinsic scatter is reliable, 
and that $M_{\rm BH}$ correlates equally well with $L_{\rm sph}$ and $L_{\rm gal}$ only for early-type galaxies, but not for all (early+late) galaxies.
%As \cite{lasker2014anal} pointed out, from the observer's perspective, measuring galaxy luminosities is obviously easier and faster 
%than performing accurate galaxy decompositions to obtain bulge luminosities. 
%This, combined with our last conclusion, suggests that one should prefer the galaxy luminosity over the bulge luminosity 
%to predict black hole masses when dealing with samples of elliptical and lenticular galaxies only.

\begin{figure}[h]
\begin{center}
\includegraphics[width=\columnwidth]{images/mbh_vs_mag_tot.pdf}
\caption{Black hole mass plotted against $3.6\rm~\mu m$ galaxy absolute magnitude. 
Symbols are coded according to the galaxy morphological type: red circle = E, red star = E/S0, 
red upward triangle = S0, blue downward triangle = S0/Sp, blue square = Sp, black diamond = merger. 
Empty symbols represent core-S\'ersic spheroids, whereas filled symbols are used for S\'ersic spheroids. 
Four spiral galaxies had their magnitudes overestimated and are shown as upper limits. 
The red dashed line indicates the BCES bisector linear regression for the 45 early-type galaxies (E+S0), 
with the red shaded area denoting its $1\sigma$ uncertainty. 
We were not able to obtain any meaningful linear regression for the 13 ($=17-4$) late-type (Sp) galaxies. 
$M_{\rm BH}$ correlates equally well with $L_{\rm sph}$ and $L_{\rm gal}$ only for early-type galaxies, 
but not for all (early+late) galaxies. }
\label{fig:mbhmaggal}
\end{center}
\end{figure}

\begin{table*}
\centering
\caption{Linear regression analysis of the $M_{\rm BH} - L_{\rm gal}$ diagram.}
\begin{tabular}{llccccc}
\tableline\tableline
{\bf Subsample (size)} & {\bf Regression} & $\boldsymbol \alpha$ & $\boldsymbol \beta$ & $\boldsymbol \langle MAG_{\rm gal} \rangle$ & $\boldsymbol \epsilon$ & $\boldsymbol \Delta$ \\ 
\tableline 
\\
  & \multicolumn{6}{l}{$\log[M_{\rm BH}/{\rm M_\odot}] = \alpha + \beta[(MAG_{\rm gal} - \langle MAG_{\rm gal} \rangle)/{\rm mag}]$} \\ [0.5em]
 All (62)               & BCES $(Y|X)$   & $8.26 \pm 0.08$ & $-0.49 \pm 0.06$ & $-24.78$ & $-$ & $0.64$ \\
                        & BCES $(X|Y)$   & $8.26 \pm 0.12$ & $-1.01 \pm 0.15$ & $-24.78$ & $-$ & $0.92$ \\
                        & BCES Bisector  & $8.26 \pm 0.09$ & $-0.72 \pm 0.07$ & $-24.78$ & $-$ & $0.71$ \\
                        & mFITEXY $(Y|X)$  & $8.26^{+0.08}_{-0.08}$ & $-0.49^{+0.06}_{-0.07}$ & $-24.78$ & $0.61^{+0.07}_{-0.06}$ & $0.64$ \\
                        & mFITEXY $(X|Y)$  & $8.26^{+0.11}_{-0.12}$ & $-1.03^{+0.13}_{-0.16}$ & $-24.78$ & $0.88^{+0.10}_{-0.08}$ & $0.93$ \\
                        & mFITEXY Bisector & $8.26^{+0.10}_{-0.10}$ & $-0.73^{+0.09}_{-0.10}$ & $-24.78$ & $-$    & $0.71$ \\
                        & {\tt linmix\_err} $(Y|X)$  & $8.26 \pm 0.09$ & $-0.49 \pm 0.07$ & $-24.78$ & $0.63 \pm 0.07$ & $0.64$ \\
                        & {\tt linmix\_err} $(X|Y)$  & $8.26 \pm 0.12$ & $-1.02 \pm 0.15$ & $-24.78$ & $0.91 \pm 0.17$ & $0.93$ \\
                        & {\tt linmix\_err} Bisector & $8.26 \pm 0.10$ & $-0.72 \pm 0.15$ & $-24.78$ & $-$    & $0.71$ \\ [0.5em]

@@

The $M_{\rm BH} - L_{\rm sph}$ diagram is shown in Figure \ref{fig:mbhmagsph}, 
and the linear regression analysis is presented in Table \ref{tab:lregsph}. \\

@@

However, the slope that we determined for S\'ersic spheroids ($M_{\rm BH} \propto L_{\rm sph}^{1.53 \pm 0.20}$) 
is notably shallower than that found by GS13 ($M_{\rm BH} \propto L_{\rm sph}^{2.73 \pm 0.55}$). 

@@

Our bulge-to-total ratios for low-luminosity S\'ersic spheroids ($3.6\rm~\mu m$ $MAG_{\rm sph} \gtrsim -22 \rm~mag$) 

@@

while the bulge-to-total ratios of GS13 were based on simple literature S\'ersic-bulge/exponential-disk decompositions 

@@

At the same time, our bulge-to-total ratios for the high-luminosity S\'ersic spheroids ($3.6\rm~\mu m$ $MAG_{\rm sph} \lesssim -24 \rm~mag$) 

@@

In this regime, the host systems are early-type galaxies that feature intermediate-scale disks\footnote{Intermediate-scale disks are 

@@

We have seen that the change in slope of the $M_{\rm BH} - L_{\rm sph}$ relation -- 

@@

We point out the unsuitability of Pearson's and Spearman's correlation coefficients because 
